%!TEX root =../mapp-challenge-18-game-book.tex
% ^ leave for LaTeXTools build functionality

\phChapterWorksheet{The Nickname Rater}{Main Puzzle 3}
% https://en.wikipedia.org/wiki/MU_puzzle

As your adventure continues, you find yourself in
\textbf{Achromatopsia City}, located at the end of Road \(20.7183-e\)
and home of the famous \textbf{Nickname Rater}.
She explains that while Trainers often like to give their
\mappMobimon{} cute nicknames, she's very particular about the rules
for an \textbf{excellent} nickname. For clarity, you can assume
that a \textbf{vowel} is any of the letters \texttt{A/E/I/O/U}, and a
\textbf{consonant} is any other English letter.

\begin{itemize}
  \item Nicknames that contain \textbf{exactly one vowel}, that is,
        \texttt{A}, \texttt{E}, \texttt{I}, \texttt{O}, and
        \texttt{U} are excellent.
  \item \textbf{Adding a consonant to the end} of an excellent nickname
        that \textbf{previously ended with a vowel}
        creates a new excellent nickname.
    \begin{itemize}
      \item Examples: If \texttt{GOLE} is excellent, then
            \texttt{GOLEN} and \texttt{GOLEK} are excellent also.
    \end{itemize}
  \item \textbf{Doubling} an excellent nickname creates a new excellent
        nickname.
    \begin{itemize}
      \item Example: If \texttt{PIKA} is excellent, then
            \texttt{PIKAPIKA} is excellent also.
    \end{itemize}
  \item \textbf{Replacing three consecutive vowels} in
        an excellent nickname \textbf{with a consonant}
        creates a new excellent nickname.
    \begin{itemize}
      \item Example: If \texttt{QUEUEBONE} is excellent, then
        \texttt{QTEBONE} and \texttt{QURBONE} are excellent also.
    \end{itemize}
  \item \textbf{Removing any double consonant} from an excellent nickname
        creates a new excellent nickname.
    \begin{itemize}
      \item Example: If \texttt{DOUGTRIO} is excellent, then
        \texttt{DOUGIO} and \texttt{DOURIO} are excellent also.
    \end{itemize}
\end{itemize}

The Nickname Rater, not one to shy away from a good \textbf{puzzle},
offers you the chance to rate the following nicknames yourself.
You'll know when you've done it correctly, because
if you \textbf{use the first letters of the excellent
nicknames below}, you will spell \textbf{another good word for a nickname}
(even if it's not particularly \textbf{excellent} itself).

% note: excellent nicknames cannot have 0(mod3) vowels

\begin{multicols}{3}
  \begin{itemize}
    % \item \texttt{PIDGEON} %non-excellent (3 vowels)
    \item \texttt{MANKAY} %4As->BA->B->BABBAB           %M
    \item \texttt{ULTRAMON} %non-excellent (3 vowels)
    \item \texttt{OMASTARE} %16As->ABABBABA             %O
    \item \texttt{VOLTEON} %non-excellent (3 vowels)
    \item \texttt{GENGASKHAN} %non-excellent (3 vowels)
    \item \texttt{EEVOL} %non-excellent (3 vowels)
    \item \texttt{NOHTYP} %16As->BABBBB                 %N
    \item \texttt{BLASTMOIST} %non-excellent (3 vowels)
    \item \texttt{ICHU} %8As->ABBA                      %I
    \item \texttt{KADABERA} %4As->BA->BABABABA          %K
    \item \texttt{AERODYCTL} %non-excellent (3 vowels)
    \item \texttt{PARACENT} %non-excellent (3 vowels)
    \item \texttt{EARSEA} %16As->AABBAABB->AABBAA       %E
    \item \texttt{DRAGONAT} %non-excellent (3 vowels)
    \item \texttt{RAGMAR} %4As->BA->BAB->BABBAB         %R
  \end{itemize}
\end{multicols}

% Include below for aucTeX integration
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mapp-challenge-18-game-book"
%%% End:
