%!TEX root =../mapp-challenge-18-game-book.tex
% ^ leave for LaTeXTools build functionality

\phChapterWorksheet{Civic Duty}{Cryptic Puzzle 1}

The \mappMobimon{} in \textbf{Wenge} are running wild, blocking the path
through Road \(\ln(148.45)\)!

All of the city utilities that
are powered by Mobimon are offline. The citizens of Wenge don't have
electricity, clean water, or even cell phone signal! \textbf{Eight utilities} have
been disrupted in total.
\begin{enumerate}
\item Electricity, powered by the lightning Mobimon \textbf{Electrumble},
\item water, powered by the moisture Mobimon \textbf{Floobles},
\item traffic lights, controlled by the temporal Mobimon \textbf{Tiktok},
\item garbage, incinerated by the flame Mobimon \textbf{Burnie},
\item cell phone access, routed by the data Mobimon \textbf{Ayepey},
\item sewage, treated by the filter Mobimon \textbf{Stankgunk},
\item street lights, controlled by the photosensitive Mobimon \textbf{Forluxi},
\item and ambulance sirens, controlled by the noisy Mobimon \textbf{Sonitus}.
\end{enumerate}


Luckily Wenge has 86 Mobimon tamers on staff and they will need \textbf{all of
  them} to restore service. They've picked up a few tricks for \textbf{how many
  tamers} should work with each different utility Mobimon.

\begin{itemize}
\item Forluxi needs the fewest tamers.
\item Tiktok needs the most tamers.
\item Ayepey and Sonitus need the same number of tamers. No other two Mobimon
  need the same number of tamers.
\item The number of tamers needed by Burnie and Forluxi differ by one.
\item Burnie and Ayepey need 9 trainers between the two of them.
\end{itemize}

The four strongest of the utility Mobimon need some \textbf{extra tricks}!

\begin{itemize}
\item Each of Electrumble, Floobles, Tiktok, and Stankgunk need a two-digit
  number of tamers.
\item Eletrumble is particularly picky, and needs a perfect square number of
  tamers.
\item Electrumble, Floobles, and Stankgunk each need an even number of tamers.
\item The number of tamers needed by Electrumble and the number of tamers needed
  by Floobles has something in \textbf{common}.
\item The number of tamers needed by Floobles and the number of tamers needed by
  Tiktok also has something in \textbf{common}.
\item The number of tamers needed by Tiktok and the number of tamers needed by
  Stankgunk also has something in \textbf{common}!
\item But the number of tamers needed by Tiktok and the number of tamers needed
  by Electrumble doesn't have much in common.
\end{itemize}

Every Mobimon adventure is about becoming the very best, and helping out the
city of Wenge should tell you something about \textbf{what kind of trait a
  Mobimon champion should have}. Also, the mayor promised to give you his
\textbf{strongest Mobimon} as a reward! Sweet!


% Include below for aucTeX integration
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mapp-challenge-18-game-book"
%%% End:
