%!TEX root =../mapp-challenge-18-game-book.tex
% ^ leave for LaTeXTools build functionality

\phSection{How do I install the ClueKeeper app?}

Visit \phUrl{http://cluekeeper.com} or visit the App Store (on iOS) or Google Play
(on Android). ClueKeeper supports iOS 9.0 or newer for iPhone and
iPad, and Android 4.1 (Jelly Bean) or newer for Android phones and tablets
as of 2017-09-21.
A Google account is required for all app users, which will be used to
create your ClueKeeper account.

\phSection{How do I set up my team?}

The first device to enter the Hunt Code provided at orientation
will be assigned as the
``master'' device, and will be the only device that can submit solutions
or check in using GPS (so make sure it has sufficient battery or a charger).

The team name may be updated by using the menu on the hunt's homepage.

Additional teammates may use the app in Read-Only mode. Using the menu on
the hunt's homepage, these teammates may be added by ClueKeeper username
or email address. Teammates can use this to review solutions and points,
but cannot submit solutions themselves. Adding teammates is completely optional.

\phSection{Do I need internet on my phone to use ClueKeeper?}

The master device will require interent to download and start the hunt,
as well as upload results at the end of the hunt. We recommend that
the master device have relatively consistent connectivity to the internet
so that teammates and Game Control will stay synced up with your team's
progress throughout the hunt.

\phSection{What can I do if I have issues using ClueKeeper?}

Players should visit Game Control if they are having trouble with
the ClueKeeper app. If Game Control cannot address the issue, then
ClueKeeper may be contacted at \texttt{admin@cluekeeper.com} or
\texttt{1-844-99-CLUES (1-844-992-5837)}.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mapp-hsc17-game-book"
%%% End:
