%!TEX root =../mapp-challenge-18-game-book.tex
% ^ leave for LaTeXTools build functionality

Thanks for downloading the puzzle booklet for \textbf{\phEventName} by
Mathematical Puzzle Programs.  These puzzle materials are provided as-is for use
in the classroom (or anywhere else!)  to help showcase the fun of mathematical
problem-solving.

When the \phEventName is over, we'd love your feedback on how to improve this
booklet. You can contact us by email at info@mappmath.org. Or better yet, submit
an issue or pull request at our GitHub page at \url{https://github.com/MaPPmath}
directly.

More information on Mathematical Puzzle Programs may be found at our website
\url{http://mappmath.org} and on our Twitter @MaPPmath. Happy mathematical puzzling!

- MaPP Directors and Volunteers

\phSection{Mathematical Puzzle Programs Leadership}
  \begin{itemize}
    \item Steven Clontz --- Director
    \item Braxton Carrigan --- Associate Director
    \item PJ Couch --- Associate Director
    \item Zachary Sarver --- Assistant Director and \phEventAbbr Game Designer
  \end{itemize}

\phSection{Attribution}

All rights to the original content in this game book are reserved by
Mathematical Puzzle Programs until the conclusion
of all \phEventName competitions.

Following the conclusion of all \phEventName competitions,
Mathematical Puzzle Programs licenses the original content in this game book
under the Creative Commons Attribution 4.0
International License. To view a copy of this license, visit

\begin{center}
  \url{http://creativecommons.org/licenses/by/4.0/}
\end{center}

More information may be found on our website at

\begin{center}
  \url{http://mappmath.org/open/}
\end{center}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mapp-hsc17-game-book"
%%% End:
