%!TEX root =../mapp-challenge-18-game-book.tex
% ^ leave for LaTeXTools build functionality

\begin{multicols}{2}
\phSection{Leagues}

Each team is registered in either the Competitive or Recreational League.
If both Leagues are playing simultaneously today at your campus, then all
scoring and awards are handled separately in both Leagues.

\phSection{Schedule}

The game officially begins at \underline{\hspace{5em}} and ends
four hours later at \underline{\hspace{5em}}. All solutions are due at
Game Control by the end of the game; late submissions will not be considered.

\phSection{Opening Puzzle}

The game begins with an Opening Puzzle to warm things up. Solving this
puzzle quickly will earn your team \textbf{5 Victory Points} and
immediately move on to the rest of the puzzles!
Don't worry about getting stuck, as all remaining
teams will be allowed to move on
at \underline{\hspace{5em}}. However, you cannot earn Victory Points for
this puzzle after that time.

\phSection{Main Puzzles}

After solving the Opening Puzzle, you will receive four
Main Puzzles. While you'll be given explicit instructions on how to
reveal the word or phrase that solves each Main Puzzle, you'll have to
rely on your mathematical modeling and problem-solving abilities to actually
make it happen. Report your solution to Game Control before the end of
the game, and your team will earn \textbf{15 Victory Points each},
for a maximum total of \textbf{60 Victory Points}.

\phSection{Bonus Puzzle}

Along with the four Main Puzzles you will be given a Bonus Puzzle. This
optimization puzzle doesn't have a unique solution, but you should still
attempt to submit the best solution you can to Game Control before the
game ends. That's because if your team is tied in
Victory Points with another team, your scores on the Bonus Puzzle will be used
to \textbf{break the tie}. You may submit up to three solutions throughout
the game (including any invalid submissions), and your best solution of the
three will be considered.

\phSection{Cryptic Puzzles}

You will be given the opportunity to solve an additional Cryptic Puzzle for
every Main Puzzle you solve. These puzzles aren't as straight-forward
as to their solution techniques, but your team might be able to use your
critical thinking to extract a hidden word or phrase. Submitting this
solution to Game Control will earn your team \textbf{5 Victory Points each},
for a maximum total of \textbf{20 Victory Points}.
Teams stuck on a Main Puzzle will get their shot eventually: all
Cryptic Puzzles will become available to all teams at \underline{\hspace{5em}},
one hour before the game ends.

\phSection{Metapuzzle}

If your team is clever enough to solve all four Cryptic Puzzles, a final
Metapuzzle will become available. A correct solution submitted to Game
Control is worth \textbf{10 Victory Points}. This puzzle will become available
to all teams at \underline{\hspace{5em}}, one hour before the game ends.

\phSection{Another Puzzle?}

Shrewd players may discover how to earn an additional
\textbf{5 Victory Points} for their team...

\phSection{Hints}

Recreational teams may ask for hints at Game Control at any time during
the game, for any Main Puzzle, Cryptic Puzzle, or Metapuzzle.
Competitive teams may only ask for hints to help with
the Main Puzzles during the final hour of the game, starting at
\underline{\hspace{5em}}. Players seeking hints should be prepared to
explain all work done on the puzzle so far, or the hint they receive may not
be useful.

\columnbreak

\phSection{Game Control}

Only one team is allowed at a time inside Game Control. If multiple teams
wish to speak to Game Control, they must form a line outside the room
and will be seen first-come, first-served. Teams that have multiple reasons
to speak to Game Control must return to the line for each reason.

\phSection{Winning the Game}

The team that earns the \textbf{most Victory Points out of 100}
by the end of the game is the \textbf{winner}. If any teams are tied,
their Bonus Puzzle scores will be used to break the tie. If that's not enough,
then the tie will be broken based on how quickly those teams earned their
Victory Points (the time each team submitted its last correct puzzle solution).
\end{multicols}

\phSection{Additional Rules}

\begin{itemize}
\item Players should not do anything which
would interfere with other teams solving puzzles. Be a good sport!
\item Submissions for each puzzle, besides the Bonus Puzzle, are unlimited.
Every submission for the Bonus Puzzle will be carefully graded by Game Control,
so only three submissions are allowed.
\item Teachers and chaperones are not allowed to help Competitive teams solve
puzzles, but they may serve as a means of communication between those teams and
Game Control when appropriate (e.g. for rules clarifications).
\item Teams may use any resources they have brought (phones, computers, etc.)
to solve puzzles, but Competitive Teams may not receive any direct
assistance from outside their team (e.g. you can't Phone a Friend).
\item Players must remain within any physical boundaries set by both
Game Control and their teacher/chaperone at all times.
\item Teachers/chaperones are responsible for their students at
all times.
\item Since this game will be played at different campuses on different
days, please do not spoil any of today's puzzles or solutions online until
the game book is released publicly on MaPPmath.org!
\item Contact Game Control immediately in the case of emergency
or any issues with these rules.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mapp-hsc17-game-book"
%%% End:
